\startcomponent annex

\environment report-environment

\starttitle[title=Annex]
\writetolist[chapter]{}{Annex}
\useURL[WafaaRepo][https://github.com/WafaaTounzi/comparison_REL][][\hyphenatedurl{https://github.com/WafaaTounzi/comparison_REL}]
All codes and repositories are provided on Github: \from[WafaaRepo]
\blank
{\bf Sentence 1}: “Blue taffeta with deeply curving serpentines in warp of the ground fabric. Between serpentines, in horizontal rows, figure of a man playing a clarinet, alternating with a bird on a slender branch. Alternate horizontal rows have sprays of flowers. Design brocaded in silver metal thread with outlines in red silk brocade.”
\blank
{\bf Sentence 2}: “For Eastern Orthodox Church. Mary holding the baby Jesus who holds a globe and makes the motion of blessing. The half figure of an angel looks toward them from the upper left corner. Continuous border on the sides and bottom of a stylized blossom (?) repeating alternately with seraphim. Top border pieced; a repeating botonee cross within a circle. Outer tape border. Metal wires and silk yarns on a red satin-silk ground. Worn and missing wires; ground worn through in some areas.”
\blank
{\bf Sentence 3}: “The perfectly matched flowing floral design gives this chasuble its distinctive appearance. The sense of liveliness in the beautiful pattern comes from the finely detailed central urn motifs, which incorporate fluting and cross-hatching; the peony blossoms shaded with subtle gradations in color; and the tulip heads that are just beginning to open.”
\blank
{\bf Sentence 4}: “Silk, silvered-metal-strip-wrapped silk, warp-float faced satin 7:1 weave of two-color complementary ground wefts with supplementary binding warps tying supplementary brocading wefts and some self-patterning ground wefts in twill interlacing, and self-patterned by areas of plain interlacing”
\stoptitle

\stopcomponent