\startcomponent contents

\environment report-environment

\startchapter[title=Conclusion]
This work is mainly based in understanding the different methods for extracting
relations between entities so that we can cumulatively extract new relation facts and expand the knowledge graph as a result, which, as a way for machines to understand the human world, has many downstream applications like question answering, recommender system and search engine.
\blank
We studied from the papers how to improve the knowledge graphs with the use of
language models and the power of deep machine learning using many tools.
Even though the outputs are what the authors were desiring, they still had weaknesses in their program and paper:
\startitemize
\item For “Language Models are Open Knowledge Graphs” The head and the tail entities are always single words, whereas many entities such as names have two or more words.
The title of the paper is a bit strongly worded and may be over-claiming what is shown quantitatively in this paper.
Their article was in-between a paper about Knowledge Base Construction (KBC) and a paper analyzing the knowledge contained within a large language model which made some confusion.
\item For OpenNRE, they may improve it by adding either new facts or it can also be generating a knowledge graph based on the relation that was predicted.
\item For FRED, since it’s using English Wikipedia as a knowledge base, they can take it to a higher level to use other languages’ data.
“Knowledge Reconciliation with Graph Convolutional Networks Paper” claims that several future directions are considered, among which is the further integration of the semantics associated with knowledge graphs.
That means FRED could be one of the choices for this improvement.
\stopitemize
As future work for SILKNOW, we would like to improve its data since it needs tools that can automatically detect relations.
We would like to do more research on prior work that already discussed Relation extraction with different methods or similar methods like the one using LMs to construct KGs (“Transformers for Automatic Knowledge Graph Construction.” By ACL 2019 / Language Models as Knowledge Bases” by EMNLP)
\stopchapter

\stopcomponent